### 2024-03-13 course/csic5011/2024/homework/homework05.tex
homework05

\lecture{Homework 5. SDP Extensions of PCA and MDS}{Yuan Yao}{Due: 2 week}{Mar. 06, 2023}

@@

\begin{enumerate}
\item Set $m=n=20$, $r=1$, and $p=0.1$, use Matlab toolbox CVX to formulate a semi-definite program for Robust PCA of $M$:
\begin{eqnarray} \label{eq:RPCA_SDP}
& \min & \frac{1}{2} (\tr(W_1)+\tr(W_2)) + \lambda \|S\|_1 \\
& s.t. & L_{ij} +S_{ij} = X_{ij}, \quad (i,j)\in E  \nonumber \\
& & \displaystyle \left[ \begin{array}{cc} 
W_1 & L \\
L^T & W_2
\end{array}
\right] \succeq 0, \nonumber
\end{eqnarray}
where you can use the matlab implementation in lecture notes as a reference;
\item Choose different parameters $p\in [0,1]$ to explore the probability of successful recover;
\item Increase $r$ to explore the probability of successful recover;
\item $^\star$ Increase $m$ and $n$ to values beyond $50$ will make CVX difficult to solve. In this case, use the Augmented Lagrange Multiplier method, e.g. in E. J. Candes, X. Li, Y. Ma, and J. Wright (2009) ``Robust Principal Component Analysis?". Journal of ACM, 58(1), 1-37. Make a code yourself (just a few lines of Matlab or Python) and test it for $m=n=1000$. A convergence criterion often used can be $\|M-\hat{L} - \hat{S} \|_F / \|M\|_F \leq \epsilon$ ($\epsilon=10^{-6}$ for example).  
\end{enumerate}

@@

\begin{enumerate}
\item Compute the true covariance matrix $\Sigma$ (and the sample covariance matrix with $n$ examples, say $n=1000$);
\item Compute the top 4 principal components of $\Sigma$ using eigenvector decomposition (by Matlab or R);
\item Use Matlab CVX toolbox to compute the first \emph{sparse} principal component by solving the SDP problem
\begin{eqnarray*}
& \max & \tr (\Sigma X) - \lambda \|X\|_1 \\
 & s.t. & \tr (X) = 1 \\
 & & X \succeq 0
\end{eqnarray*}
Choose $\lambda =0$ and other positive numbers to compare your results with normal PCA;

>>>>

\lecture{Homework 5. SDP Extensions of PCA and MDS}{Yuan Yao}{Due: 1 week}{Mar. 13, 2024}

@@

\begin{enumerate}
\item Set $m=n=20$, $r=1$, and $p=0.1$, use Matlab toolbox CVX or its Python version CVXPY (\url{https://www.cvxpy.org/install/index.html}) to formulate a semi-definite program for Robust PCA of $M$:
\begin{eqnarray} \label{eq:RPCA_SDP}
& \min & \frac{1}{2} (\tr(W_1)+\tr(W_2)) + \lambda \|S\|_1 \\
& s.t. & L_{ij} +S_{ij} = X_{ij}, \quad (i,j)\in E  \nonumber \\
& & \displaystyle \left[ \begin{array}{cc} 
W_1 & L \\
L^T & W_2
\end{array}
\right] \succeq 0, \nonumber
\end{eqnarray}
where you can use the matlab implementation in lecture notes as a reference;
\item Choose different parameters $p\in [0,1]$ to explore the probability of successful recover;
\item Increase $r$ to explore the probability of successful recover;
\item $^\star$ Increase $m$ and $n$ to values beyond $50$ will make CVX difficult to solve. In this case, use the Augmented Lagrange Multiplier method, e.g. in E. J. Candes, X. Li, Y. Ma, and J. Wright (2009) ``Robust Principal Component Analysis?". Journal of ACM, 58(1), 1-37. Make a code yourself (just a few lines of Matlab or Python) and test it for $m=n=1000$. A convergence criterion often used can be $\|M-\hat{L} - \hat{S} \|_F / \|M\|_F \leq \epsilon$ ($\epsilon=10^{-6}$ for example).  
\end{enumerate}

@@

\begin{enumerate}
\item Compute the true covariance matrix $\Sigma$ (and the sample covariance matrix with $n$ examples, say $n=1000$);
\item Compute the top 4 principal components of $\Sigma$ using eigenvector decomposition;
\item Use Matlab CVX toolbox or Python CVXPY to compute the first \emph{sparse} principal component by solving the SDP problem
\begin{eqnarray*}
& \max & \tr (\Sigma X) - \lambda \|X\|_1 \\
 & s.t. & \tr (X) = 1 \\
 & & X \succeq 0
\end{eqnarray*}
Choose $\lambda =0$ and other positive numbers to compare your results with normal PCA;
